%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}


%----------FONT OPTIONS----------
% sans-serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage{helvet}
%\renewcommand*\familydefault{\sfdefault}

%\usepackage[default]{sourcesanspro}

% serif
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlist[itemize]{leftmargin=1.5cm}

% Sections formatting
\titleformat{\section}{
  \vspace{-15pt}\raggedright%\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-5pt}}
  }
}

\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\newcommand{\resumeSubheading}[3]{
    \begin{center}
    \begin{tabularx}{1\textwidth}{XP{9.4cm}r}
      \small\textbf{#1} & \textbf{#2} & \textbf{#3}
    \end{tabularx}\vspace{-7pt}
    \end{center}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

%\renewcommand\labelitemii{$\vcenter{\hbox{\large\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={\large\textbullet}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{10pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\iffalse
\begin{center}
    \textbf{\Huge \scshape Ben Lancaster} \\ \vspace{5pt}
    \small (+44) 07722 358258 $|$ \href{mailto:ben@bendl.me}{\underline{ben@bendl.me}} $|$ 
    \href{https://uk.linkedin.com/in/bendl}{\underline{uk.linkedin.com/in/bendl}} $|$
    \href{https://github.com/bendl}{\underline{github.com/bendl}}
\end{center}
\fi

%\iffalse
\begin{minipage}{4in}
    \textbf{\Huge Ben Lancaster}\\
    07722 358258 \href{mailto:ben@bendl.me}{ben@bendl.me}\\
    England, United Kingdom
\end{minipage}
    \hfill
\begin{minipage}{3in}
\begin{flushright}
    \href{https://uk.linkedin.com/in/bendl}{https://uk.linkedin.com/in/bendl}\\
    \href{https://github.com/bendl}{https://github.com/bendl}  \\
    \href{https://bendl.me}{https://bendl.me}
\end{flushright}
\end{minipage}
\vspace{15pt}
%\fi

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
    \begin{tabularx}{1\textwidth}{p{8cm}Xr}
      \small\textbf{RTL Design Engineer} & \small\textbf{ARM Limited} & \small\textbf{September 2019 -- present}
    \end{tabularx}\vspace{-3pt}
    %\resumeSubheading{RTL Design Engineer}{ARM Limited}{September 2019 -- present}
    \resumeItemListStart
        \resumeItem{Design and verification of various Systems and Interconnect IP using SystemVerilog.}
        \resumeItem{IP requirements capture and specification.}
        \resumeItem{Programmers-view RTL for memory-mapped peripherals.}
        \resumeItem{Automation and rendering flows for generating RTL/UVM from machine-readable specifications.}
        \resumeItem{Physical implementation trials using Cadence and Synopsys tooling flows.}
        \resumeItem{Verification of AMBA protocols and other on-chip interfaces.}
    \resumeItemListEnd

    \begin{tabularx}{1\textwidth}{p{7cm}Xr}
      \small\textbf{Firmware Engineer, Placement} & \small\textbf{Spirent Communications} & \small\textbf{June 2016 -- August 2017}  \\
    \end{tabularx}\vspace{-3pt}
    %\resumeSubheading{Firmware Engineer, Placement}{Spirent Communications}{June 2016 -- August 2017}
        \resumeItemListStart
        \resumeItem{Embedded programming on Xilinx MicroBlaze FPGAs and PIC16/24 microcontrollers.}
\resumeItem{Implemented on-chip power levelling and calibration for GNSS RF signal generators.}
\resumeItem{Controlling on-board fans, LEDs, EEPROM, and other peripherals with I2C and SMBus.}
\resumeItem{Configuring, building, and maintaining Embedded Linux distributions using Yocto.}
\resumeItem{Linux USB kernel driver development.}
    \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


%-----------EDUCATION-----------
\section{EDUCATION}
    \begin{tabularx}{1\textwidth}{p{7.8cm}Xr}
      \small\textbf{MSc (Eng) Embedded Systems Engineering} & \small\textbf{University of Leeds} & \small\textbf{2018-2019} \\
    \end{tabularx}\vspace{-3pt}
    \resumeItemListStart
\resumeItem{86\%, Final Project: Multi-core RISC SoC Design and Implementation for FPGAs.}
\resumeItem{Courses include: FPGA Design for System-on-Chip, Digital Signal Processing for Communications,
Embedded Microprocessor System Design, Circuits, Medical Electronics and E-Health}
    \resumeItemListEnd
    %\resumeSubheading{MSc (Eng) Embedded Systems Engineering}{University of Leeds}{2018-2019}
    
    \begin{tabularx}{1\textwidth}{p{7.5cm}Xr}
      \small\textbf{BSc (Hons) Computer Science} & \small\textbf{University of Plymouth} & \small\textbf{2014 – 2018}  \\
    \end{tabularx}\vspace{-3pt}
    \resumeItemListStart
    \resumeItem{Top Final Year Student, Best Final Project, Revell Research Systems Price}
\resumeItem{Final Project: FPGA-based 16-bit RISC soft-microprocessor (with IO \& interrupts) and Compiler.}
\resumeItem{First Class Honours with Certificate of Professional Industrial Experience.}
\resumeItem{Courses: Digital Electronics, Embedded Systems and Compilers, Machine Vision, Parallel Computation.}
    \resumeItemListEnd
    %\resumeSubheading{MSc (Eng) Embedded Systems Engineering}{University of Leeds}{2018-2019}


%-----------PROJECTS-----------
\section{OPEN-SOURCE PROJECTS \& CONTRIBUTIONS}
    \resumeItemListStart
\resumeItem{Multi-core RISC System-on-Chip bendl/vmicro16 Up to 96 cores on Spartan-6 and Cyclone V FPGAs.}
\resumeItem{16-bit RISC soft-microprocessor bendl/prco304 An FPGA-based RISC soft-microprocessor written in
Verilog, complete with Compiler and programming language.}
\resumeItem{ARM Cortex M0 Processor Board bendl/armm0 A 2-layer board for the Minispartan6+ FPGA
development kit. Features an STM32F0 TSSOP processor, dual power supplies, I2C, ICSP, and LEDs.}
    \resumeItemListEnd

%-----------AWARDS-----------
\section{ADDITIONAL EXPERIENCE \& AWARDS}
    \vspace{-15pt}
\begin{multicols}{2}
    \resumeItemListStart
    \resumeItem{Top Final Year Student}
    \resumeItem{Best Final Project}
    \resumeItemListEnd
\columnbreak
    \resumeItemListStart
    \resumeItem{Dean’s List 2015-2018 member}
    \resumeItem{Revell Research Systems Prize}
    \resumeItemListEnd
\end{multicols}\vspace{5pt}

%-----------PROJECTS-----------
\section{TECHNOLOGIES}
    \resumeItemListStart
\resumeItem{Digital Design, CMOS, IC Design}
\resumeItem{IP Integration}
\resumeItem{Verilog, SystemVerilog}
\resumeItem{Cadence, Xilinx/Altera FPGAs, Vivado/ISE, Quartus, }
\resumeItem{C, C++, Python, Linux (user + kernel), Bash, Make, CUDA}
    \resumeItemListEnd


%-------------------------------------------
\end{document}
